A practical look at genetic algorithms

### 2015-11-29 evolutionaryComputation/practicals/report.tex
added a bunch of text going trough the entire architecture.

\subsection{Architecture}
\begin{figure}[ht!]
\centering
\begin{emp}[classdiag](20,20)
Class.mem("Member")("+Fitness:Int", "+genes:String")();
Class.pop("Population")("+members:Seq[Member]", "+factory:String=>Member")();
Class.pairedPop("PairedPopulation")("+members:Seq[Pair]","+factory:String=>Member")(
"+pairedToPop(how):Population");
Class.pai("Pair")("+father:Member","+mother:Member")();

@@

@@

\begin{figure}[ht!]
\centering
\begin{emp}[classdiag](20,20)
Class.ex("Experiment")(
	"+name:String",
	"+variation:String",
	"evolution: Evolution",
	"factory:String => IMember"
)();
Class.result("RunResult")(
	"popSize:Int",
	"success:Boolean",
	"runtime:Long",
	"generationCount:Int",
	"fitnessCallCount:Int"
	)();
Class.stoastic("StoasticRun")(
	"runs:Seq[RunResult]",
	"required:Int",
	)();
topToBottom.left(20)(ex,result,stoastic);
drawObjects(ex,result,stoastic);
\end{emp}
\caption{Experiment}
\end{figure}

>>>>

\subsection{Architecture}
The code is split up into 4 parts I'll go trough them in the rough order
they were implemented. First there are the case classes. These are
imutable classes that hold the domain information (Java pojos).
Then there are the algoritm classes and objects. These are pretty straight
forward logical structures. After that comes the expirment and the result
classes. And finally there is the presentation object Main. the only thing it does
is interpit the experiment in this case into a latex structure.

\begin{figure}[ht!]
\centering
\begin{emp}[classdiag](20,20)
Class.mem("Member")("+Fitness:Int", "+genes:String")();
Class.pop("Population")("+members:Seq[Member]", "+factory:String=>Member")();
Class.pairedPop("PairedPopulation")("+members:Seq[Pair]","+factory:String=>Member")(
"+pairedToPop(how):Population");
Class.pai("Pair")("+father:Member","+mother:Member")();

@@

The case classses add meaning to the structures. They also provide an API.
A case class is a scala concept were you just define the atributes and
equals, hascode and tostring methods are generated for you. They're also
by default imutable, which is something I kept intact.

The member is something with a gene.
These are generated in batches into a population,
a population will also have a function with it to generate new members.
The population class doesn't use it itself, but when its members are paired
up into \emph{Pair}'s. A \emph{PairedPopulation} can use the creation function
of the original population to create new members. The PairedPopulation has
also a utitity function pairedToPop, this receives a how, in which it can
insert zipped genes (char by char paired up strings) and from which comes
a charsequence. This how is usually implemented by one of the crossing methods.
But the code around this 'how' was always the same, so paired population
abstracted it away. The resulting string is then inserted into a member
factory to create a new member (the member factory then allows mutation
or obfuscation of the genes).

@@

The evolution class is the general stucture of a GA{.} It's very simple and
basically follows the steps from the slides:
\begin{enumerate}
	\item Select mates.
	\item Generate offspring.
	\item Select the fittests.
\end{enumerate}

To construct an Evolution you need to pass a valuation function, a mateselector.
An offspring gnerator, a fittestfilter. And a function that determines if there
is a good enough solution in the current population.

The step calls almost all given functions in above order except for has good
enough solution. This function is called in genitic, which will continue
calling steps until the population is good enough, or until parents
and children are equal. The population is a case class, so
the generated comperison method is used to check if the children and parents
are equal. Startgenetic makes a seq of population and calls genetic.

The objects defined above all have functions with the types same named evolution
atributes. So the functions are just basically options you can use to create an
evolution from. The only exception is the withCoinFlipMutation function in
memberFactories. This function acts as a decorating function. So you can wrap
it around another function to create a new function.
Objects are just singletons, or Java static space. Allmost all the functions
in these objects are `pure', this means they get some input and create some
output without any side effects. This is not true for the factories, which
use random, and the offspring generators, which also use random. It's also
not true for tournement elitism, this suffles randomly.

\begin{figure}[ht!]
\centering
\begin{emp}[classdiag](20,20)
Class.ex("Experiment")(
	"+name:String",
	"+variation:String",
	"evolution: Evolution",
	"factory:String => IMember"
)(
	"+bisectionalSearch():StoasticRun",
	"verifyLowest(currentPop:Int,faults:Int,index:Int):Seq[RunResult]",
	"findOptimum(consideringSize:Int,difference:Int):Seq[RunResult]",
	"run(consideringSize:Int):RunResult"
);
Class.result("RunResult")(
	"+popSize:Int",
	"+success:Boolean",
	"+runtime:Long",
	"+generationCount:Int",
	"+fitnessCallCount:Int"
	)();
Class.stoastic("StoasticRun")(
	"+runs:Seq[RunResult]",
	"+required:Int",
	)();
topToBottom.left(20)(ex,stoastic);
leftToRight.top(20)(stoastic,result);
drawObjects(ex,result,stoastic);

link(association)(stoastic.e -- result.w);
item(iAssoc)("*")(obj.ne = result.w);
\end{emp}
\caption{Experiment}
\end{figure}
